### 2024-05-03 texts/paper_closing.tex
paper update after PMDB update

% Created 2024-04-23 di 20:31
% Intended LaTeX compiler: pdflatex
\documentclass[12pt]{article}

@@

@@

% latex table generated in R 4.3.3 by xtable 1.8-4 package
% Tue Apr 23 17:09:15 2024
\begin{table}[ht]
\centering
\begin{tabular}{lrll}
  \hline 
 \multicolumn{1}{l}{Self-identification} & \multicolumn{1}{l}{N} & \multicolumn{1}{l}{Self-ID (recoded)} & \multicolumn{1}{l}{examples}\\ 
 \hline
 Museum & 177 & Museum & Museum Kampa, Museum Barberini \\ 
  Foundation & 101 & Foundation & Marciano Art Foundation, Hill Art Foundation \\ 
  Collection &  74 & Collection & The Farjam Collection, Sammlung Boros \\ 
  None &  56 & Other & The Bunker, The Broad \\ 
  Center &  17 & Other & Dairy Art Centre, Art Center Nabi \\ 
  Art space &  12 & Other & El Espacio 23, Qiao Space \\ 
  Gallery &  11 & Other & Saatchi Gallery, Galerie C15 \\ 
  House / villa &  10 & Other & Villa La Fleur, Casa Daros Rio \\ 
  Institute &   9 & Other & Instituto Inhotim, Woods Art Institute \\ 
  Kunsthalle &   7 & Other & Kunsthalle Würth, G2 Kunsthalle \\ 
  Park / garden &   4 & Other & Schlosspark Eyebesfeld, Il Giardino dei Lauri \\ 
   \hline
\end{tabular}
\caption{Selfidentification} 
\label{tbl:t_selfid}
\end{table}

@@

% latex table generated in R 4.3.3 by xtable 1.8-4 package
% Tue Apr 23 17:09:14 2024
\begin{table}[ht]
\centering
\begin{tabular}{llrrrrrr}
  \hline
 & & \multicolumn{2}{c}{Museum} & \multicolumn{4}{c}{Museum-year} \\ 
\cmidrule(r){3-4}\cmidrule(r){5-8} \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{Count} & \multicolumn{1}{l}{Mean} & \multicolumn{1}{l}{Mean} & \multicolumn{1}{l}{SD} & \multicolumn{1}{l}{Min.} & \multicolumn{1}{l}{Max.}\\ 
 \hline
  \multicolumn{8}{l}{\textbf{Founder}} \\ 
 & Gender - Male & 274 & 0.573 & 5.9e-01 &   0.49 & 0 & 1 \\ 
   & Gender - Female & 76 & 0.159 & 1.7e-01 &   0.38 & 0 & 1 \\ 
   & Gender - Couple & 128 & 0.268 & 2.4e-01 &   0.43 & 0 & 1 \\ 
   & Founder died & 57 & 0.119 & 9.3e-02 &   0.29 & 0 & 1 \\ 
   \multicolumn{8}{l}{\textbf{Museum}} \\ 
 & Self-Identification - Museum & 177 & 0.370 & 4.0e-01 &   0.49 & 0 & 1 \\ 
   & Self-Identification - Foundation & 101 & 0.211 & 1.9e-01 &   0.39 & 0 & 1 \\ 
   & Self-Identification - Collection & 74 & 0.155 & 1.4e-01 &   0.35 & 0 & 1 \\ 
   & Self-Identification - Other & 126 & 0.264 & 2.6e-01 &   0.44 & 0 & 1 \\ 
   & Founder name in Museum name & 228 & 0.477 & 4.8e-01 &   0.50 & 0 & 1 \\ 
   & MOW inclusion & 91 & 0.190 & 2.8e-01 &   0.45 & 0 & 1 \\ 
   & AN Ranking - Not Included &  &  & 8.0e-01 &   0.40 & 0 & 1 \\ 
   & AN Ranking - Included &  &  & 1.5e-01 &   0.36 & 0 & 1 \\ 
   & AN Ranking - Dropped &  &  & 5.6e-02 &   0.23 & 0 & 1 \\ 
   & Exhibition any &  &  & 6.5e-01 &   0.48 & 0 & 1 \\ 
   & Exhibition any last 5 years &  &  & 4.7e-01 &   0.50 & 0 & 1 \\ 
   & PC1 (Size) & 74.6913323980041 & 0.156 & 1.3e-01 &   1.88 & -6.4 & 2.62 \\ 
   & PC2 (Support) & 58.6876842646085 & 0.123 & 1.6e-01 &   1.50 & -5 & 2.74 \\ 
   \multicolumn{8}{l}{\textbf{Environment}} \\ 
 & PM density (country) &  &  & 4.3e-01 &   1.28 & 0.00077 & 27.26 \\ 
   & Pop. (millions) within 10km &  &  & 1.3e+00 &   1.70 & 0.000087 & 10.81 \\ 
   & Pop. (millions) country &  &  & 1.6e+02 & 297.59 & 0.037 & 1412.36 \\ 
   & Nbr PM within 10km &  &  & 1.7e+00 &   3.07 & 0 & 15 \\ 
   & PM density (10km) &  &  & 1.5e+00 &   4.15 & 0 & 41.85 \\ 
   & Europe and North America & 311 & 0.651 & 6.5e-01 &   0.48 & 0 & 1 \\ 
   & Region - Africa & 7 & 0.015 & 1.2e-02 &   0.11 & 0 & 1 \\ 
   & Region - Asia & 128 & 0.268 & 2.8e-01 &   0.45 & 0 & 1 \\ 
   & Region - Europe & 241 & 0.504 & 5.1e-01 &   0.50 & 0 & 1 \\ 
   & Region - Latin America & 22 & 0.046 & 4.4e-02 &   0.20 & 0 & 1 \\ 
   & Region - North America & 70 & 0.146 & 1.4e-01 &   0.35 & 0 & 1 \\ 
   & Region - Oceania & 10 & 0.021 & 1.9e-02 &   0.14 & 0 & 1 \\ 
   & year &  &  & 2.0e+03 &   5.75 & 2000 & 2021 \\ 
   & Time Period 2000-2004 &  &  & 1.0e-01 &   0.30 & 0 & 1 \\ 
   & Time Period 2005-2009 &  &  & 1.7e-01 &   0.37 & 0 & 1 \\ 
   & Time Period 2010-2014 &  &  & 2.6e-01 &   0.44 & 0 & 1 \\ 
   & Time Period 2015-2019 &  &  & 3.3e-01 &   0.47 & 0 & 1 \\ 
   & Time Period 2020-2024 &  &  & 1.5e-01 &   0.35 & 0 & 1 \\ 
   \hline
\end{tabular}
\caption{Summary Statistics} 
\label{tbl:t_sumstats}
\end{table}

@@

Overall the entire life span, the average hazard rate is 0.77\%, which allows comparison to other studies of NPO closure.
While I did not find a systematic literature review or meta-analysis, a number of individual studies had investigated similar populations based on IRS data (see table \ref{tbl:litreview})

\begin{table}[htbp]
\caption{\label{tbl:litreview}Hazard rates in studies of museums art Art NPOs}
\centering
\begin{tabular}{llll}
\hline
study & population & avg. hazard rate & org years\\
\hline
\cite{Hager_2001_vulnerability} & Art Museums & 2.4\% & \\
\cite{Gordon_etal_2013_insolvency} & Museums & 0.7\% & \\
\hline
\cite{Hager_2001_vulnerability} & all Art NPOs & 2.8\% & \\
\cite{Gordon_etal_2013_insolvency} & all Art NPOs & 2.08\% & \\
\hline
\end{tabular}
\end{table}

@@

Comparison to other forms of nonprofit organizations reported by \parencite{Gordon_etal_2013_insolvency}
places private museum at a risk similar to that of animal shelters and zoos (0.7\%), botanical \& environmental centers (0.8\%), colleges and universities (0.8\%), food and agricultural-oriented human service organizations (0.8\%) and  student and educational services (0.8\%).
While the diversity of non-profit organizations makes comparisons to its entirety difficult, it is still worthwhile to consider that the average hazard of private museums 0.77\% is around half that of that NPOs generally (1.58\%, see table \ref{tbl:litreview2} for studies on wider nonprofit populations).
It is furthermore substantially lower than that of youth centers (1.4\%), children-focused human services (2.4\%), K12 schools (1.8\%), mental health organizations (2.4\%) or performing arts organizations (3.7\%).
In fact, lower dissolution rates are only reported for historical societies (0.5\%) and libraries (0.2\%).

\begin{table}[htbp]
\caption{\label{tbl:litreview2}Hazard rates in studies of NPOs}
\centering
\begin{tabular}{llll}
\hline
study & population & avg. hazard rate & data source\\
\hline
\cite{Gordon_etal_2013_insolvency} & NPOs & 1.58\% & IRS\\
\cite{Hager_Galaskiewicz_Larson_2007_liability} & NPOs & 1.25\% & own data\\
\cite{Clifford_2018_reinforcing} & Charities & 2\%-5\% & Reg. of Charities (UK)\\
\cite{Mayer_2022_slimmer} & public charities & 0.17\% & IRS\\
\hline
\end{tabular}
\end{table}

@@

% latex table generated in R 4.3.3 by xtable 1.8-4 package
% Tue Apr 23 20:19:31 2024
\begin{table}[ht]
\centering
\begin{tabular}{p{0mm}lD{)}{)}{8)3}}
  \hline 
 \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{r\_pop4}\\ 
 \hline
  \multicolumn{3}{l}{\textbf{Founder}} \\ 
 & Gender - Female & .16 \; (0.37) \\ 
   & Gender - Couple & .17 \; (0.36) \\ 
   & Founder died & -.06 \; (0.57) \\ 
   \multicolumn{3}{l}{\textbf{Museum}} \\ 
 & Self-Identification - Foundation & .91 \; (0.49) \\ 
   & Self-Identification - Collection & .33 \; (0.59) \\ 
   & Self-Identification - Other & 1.44 \; (0.39)^{***} \\ 
   & AN Ranking - Included & .27 \; (0.38) \\ 
   & AN Ranking - Dropped & .76 \; (0.52) \\ 
   & Founder name in Museum name & -.41 \; (0.33) \\ 
   & Exhibition any & .13 \; (0.33) \\ 
   \multicolumn{3}{l}{\textbf{Environment}} \\ 
 & PM density (country) & .59 \; (0.46) \\ 
   & PM density$^{2}$ (country) & -.02 \; (0.02) \\ 
   & Pop. (millions) within 10km & .31 \; (0.11)^{**} \\ 
   & Nbr PM within 10km & .28 \; (0.09)^{**} \\ 
   & Nbr PM (10km) * Pop (10km) & -.10 \; (0.04)^{**} \\ 
   & Great Recession (2008/09) & -1.21 \; (1.02) \\ 
   & Covid Pandemic (2020/21) & .27 \; (0.34) \\ 
   \hline
 & Museum-years & 5862 \\ 
   & Closures & 51 \\ 
   & log. Likelihood & -244.54 \\ 
   & AIC & 523.08 \\ 
   & BIC & 555.92 \\ 
   \hline 
 \multicolumn{3}{l}{\footnotesize{standard errors in parantheses.\textsuperscript{***}p $<$ 0.001;\textsuperscript{**}p $<$ 0.01;\textsuperscript{*}p $<$ 0.05.}}
\end{tabular}
\caption{Cox Proportional Hazards Regression Results} 
\label{tbl:t_reg_coxph}
\end{table}

>>>>

% Created 2024-05-03 vr 10:56
% Intended LaTeX compiler: pdflatex
\documentclass[12pt]{article}

@@

resource-based: lack of audience, or many other people competing for audience
\cite{Velthuis_Gera_forthcoming_fragility}:
p.23: In other cases, the location of the museum is a factor in limited visitor interest. On the
one hand, private museums located in metropolitan art centers tend to face competition over
visitors  from  well-established  other  museums  in  the  vicinity.  On  the  other  hand,  private
museums located outside of those centers can be confronted with a small local audience, and
difficulties in attracting visitors from afar.

@@

% latex table generated in R 4.3.3 by xtable 1.8-4 package
% Fri May  3 10:55:27 2024
\begin{table}[ht]
\centering
\begin{tabular}{lrll}
  \hline 
 \multicolumn{1}{l}{Self-identification} & \multicolumn{1}{l}{N} & \multicolumn{1}{l}{Self-ID (recoded)} & \multicolumn{1}{l}{examples}\\ 
 \hline
 Museum & 190 & Museum & Museum Kampa, Museum Barberini \\ 
  Foundation & 104 & Foundation & Marciano Art Foundation, Hill Art Foundation \\ 
  Collection &  69 & Collection & The Farjam Collection, Sammlung Boros \\ 
  None &  64 & Other & The Bunker, The Broad \\ 
  Center &  17 & Other & Dairy Art Centre, Art Center Nabi \\ 
  Gallery &  14 & Other & Saatchi Gallery, Galerie C15 \\ 
  Art space &  13 & Other & El Espacio 23, Qiao Space \\ 
  House / villa &  11 & Other & Villa La Fleur, Casa Daros Rio \\ 
  Institute &  10 & Other & Instituto Inhotim, Woods Art Institute \\ 
  Kunsthalle &   8 & Other & Kunsthalle Würth, G2 Kunsthalle \\ 
  Park / garden &   3 & Other & Schlosspark Eyebesfeld, Il Giardino dei Lauri \\ 
   \hline
\end{tabular}
\caption{Selfidentification} 
\label{tbl:t_selfid}
\end{table}

@@

% latex table generated in R 4.3.3 by xtable 1.8-4 package
% Fri May  3 10:55:26 2024
\begin{table}[ht]
\centering
\begin{tabular}{llrrrrrr}
  \hline
 & & \multicolumn{2}{c}{Museum} & \multicolumn{4}{c}{Museum-year} \\ 
\cmidrule(r){3-4}\cmidrule(r){5-8} \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{Count} & \multicolumn{1}{l}{Mean} & \multicolumn{1}{l}{Mean} & \multicolumn{1}{l}{SD} & \multicolumn{1}{l}{Min.} & \multicolumn{1}{l}{Max.}\\ 
 \hline
  \multicolumn{8}{l}{\textbf{Founder}} \\ 
 & Gender - Male & 294 & 0.584 & 6.0e-01 &   0.49 & 0 & 1 \\ 
   & Gender - Female & 79 & 0.157 & 1.7e-01 &   0.37 & 0 & 1 \\ 
   & Gender - Couple & 130 & 0.258 & 2.3e-01 &   0.42 & 0 & 1 \\ 
   & Founder - alive & 440 & 0.875 & 9.0e-01 &   0.30 & 0 & 1 \\ 
   & Founder - died recently & 17 & 0.034 & 1.9e-02 &   0.13 & 0 & 1 \\ 
   & Founder - died 2+ years ago & 46 & 0.091 & 7.9e-02 &   0.27 & 0 & 1 \\ 
   \multicolumn{8}{l}{\textbf{Museum}} \\ 
 & Self-Identification - Museum & 190 & 0.378 & 4.1e-01 &   0.49 & 0 & 1 \\ 
   & Self-Identification - Foundation & 104 & 0.207 & 1.9e-01 &   0.39 & 0 & 1 \\ 
   & Self-Identification - Collection & 69 & 0.137 & 1.3e-01 &   0.34 & 0 & 1 \\ 
   & Self-Identification - Other & 140 & 0.278 & 2.7e-01 &   0.45 & 0 & 1 \\ 
   & Founder name in Museum name & 240 & 0.477 & 4.8e-01 &   0.50 & 0 & 1 \\ 
   & MOW inclusion & 92 & 0.183 & 2.7e-01 &   0.45 & 0 & 1 \\ 
   & AN Ranking - Not Included &  &  & 8.0e-01 &   0.40 & 0 & 1 \\ 
   & AN Ranking - Included &  &  & 1.4e-01 &   0.35 & 0 & 1 \\ 
   & AN Ranking - Dropped &  &  & 5.3e-02 &   0.23 & 0 & 1 \\ 
   & Exhibition any &  &  & 6.3e-01 &   0.48 & 0 & 1 \\ 
   & Exhibition any last 5 years &  &  & 4.6e-01 &   0.50 & 0 & 1 \\ 
   & PC1 (Size) & 112.930441195886 & 0.225 & 1.8e-01 &   1.90 & -6.5 & 2.61 \\ 
   & PC2 (Support) & 90.555299883145 & 0.180 & 2.0e-01 &   1.52 & -5.1 & 2.71 \\ 
   \multicolumn{8}{l}{\textbf{Environment}} \\ 
 & PM density (country) &  &  & 4.5e-01 &   1.26 & 0.00077 & 27.26 \\ 
   & Pop. (millions) within 10km &  &  & 1.3e+00 &   1.68 & 0.000087 & 10.81 \\ 
   & Pop. (millions) country &  &  & 1.6e+02 & 292.68 & 0.037 & 1412.36 \\ 
   & Nbr PM within 10km &  &  & 1.8e+00 &   3.14 & 0 & 16 \\ 
   & PM density (10km) &  &  & 1.7e+00 &   4.93 & 0 & 76.37 \\ 
   & Europe and North America & 320 & 0.636 & 6.4e-01 &   0.48 & 0 & 1 \\ 
   & Region - Africa & 8 & 0.016 & 1.2e-02 &   0.11 & 0 & 1 \\ 
   & Region - Asia & 142 & 0.282 & 2.9e-01 &   0.45 & 0 & 1 \\ 
   & Region - Europe & 248 & 0.493 & 5.0e-01 &   0.50 & 0 & 1 \\ 
   & Region - Latin America & 23 & 0.046 & 4.2e-02 &   0.20 & 0 & 1 \\ 
   & Region - North America & 72 & 0.143 & 1.4e-01 &   0.34 & 0 & 1 \\ 
   & Region - Oceania & 10 & 0.020 & 1.9e-02 &   0.13 & 0 & 1 \\ 
   & year &  &  & 2.0e+03 &   5.72 & 2000 & 2021 \\ 
   & Time Period 2000-2004 &  &  & 1.0e-01 &   0.30 & 0 & 1 \\ 
   & Time Period 2005-2009 &  &  & 1.7e-01 &   0.37 & 0 & 1 \\ 
   & Time Period 2010-2014 &  &  & 2.6e-01 &   0.44 & 0 & 1 \\ 
   & Time Period 2015-2019 &  &  & 3.3e-01 &   0.47 & 0 & 1 \\ 
   & Time Period 2020-2024 &  &  & 1.4e-01 &   0.35 & 0 & 1 \\ 
   & Great Recession (2008/09) &  &  & 7.6e-02 &   0.27 & 0 & 1 \\ 
   & Covid Pandemic (2020/21) &  &  & 1.4e-01 &   0.35 & 0 & 1 \\ 
   \hline
\end{tabular}
\caption{Summary Statistics} 
\label{tbl:t_sumstats}
\end{table}

@@

Overall the entire life span, the average hazard rate is 0.87\%, which allows comparison to other studies of NPO closure.
While I did not find a systematic literature review or meta-analysis, a number of individual studies had investigated similar populations based on IRS data (see table \ref{tbl:litreview})

\begin{table}[htbp]
\caption{\label{tbl:litreview}Hazard rates in studies of museums and art NPOs}
\centering
\begin{tabular}{lll}
\hline
study & population & avg. hazard rate\\
\hline
\cite{Hager_2001_vulnerability} & Art Museums & 2.4\%\\
\cite{Gordon_etal_2013_insolvency} & Museums & 0.7\%\\
\cite{Bowen_1994_charitable} & Museums & 1.1\%\\
\hline
\cite{Hager_2001_vulnerability} & all Art NPOs & 2.8\%\\
\cite{Gordon_etal_2013_insolvency} & all Art NPOs & 2.08\%\\
\hline
\end{tabular}
\end{table}

@@

Comparison to other forms of nonprofit organizations reported by \parencite{Gordon_etal_2013_insolvency}
places private museum at a risk similar to that of animal shelters and zoos (0.7\%), botanical \& environmental centers (0.8\%), colleges and universities (0.8\%), food and agricultural-oriented human service organizations (0.8\%) and  student and educational services (0.8\%).
While the diversity of non-profit organizations makes comparisons to its entirety difficult, it is still worthwhile to consider that the average hazard of private museums 0.87\% is around half that of that NPOs generally (1.58\%, see table \ref{tbl:litreview2} for studies on wider nonprofit populations).
It is furthermore substantially lower than that of youth centers (1.4\%), children-focused human services (2.4\%), K12 schools (1.8\%), mental health organizations (2.4\%) or performing arts organizations (3.7\%).
In fact, lower dissolution rates are only reported for historical societies (0.5\%) and libraries (0.2\%).

\begin{table}[htbp]
\caption{\label{tbl:litreview2}Hazard rates in studies of NPOs}
\centering
\begin{tabular}{llll}
\hline
study & population & avg. hazard rate & data source\\
\hline
\cite{Gordon_etal_2013_insolvency} & NPOs & 1.58\% & IRS\\
\cite{Hager_Galaskiewicz_Larson_2007_liability} & NPOs & 1.25\% & own data\\
\cite{Clifford_2018_reinforcing} & Charities & 2\%-5\% & Reg. of Charities (UK)\\
\cite{Mayer_2022_simmer} & public charities & 0.17\% & IRS\\
\hline
\end{tabular}
\end{table}

@@

% latex table generated in R 4.3.3 by xtable 1.8-4 package
% Fri May  3 10:55:34 2024
\begin{table}[ht]
\centering
\begin{tabular}{p{0mm}lD{)}{)}{8)3}}
  \hline 
 \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{r\_pop4}\\ 
 \hline
  \multicolumn{3}{l}{\textbf{Founder}} \\ 
 & Gender - Female & .02 \; (0.34) \\ 
   & Gender - Couple & -.10 \; (0.32) \\ 
   & Founder - died recently & 1.09 \; (0.61) \\ 
   & Founder - died 2+ years ago & -.06 \; (0.55) \\ 
   \multicolumn{3}{l}{\textbf{Museum}} \\ 
 & Self-Identification - Foundation & .25 \; (0.42) \\ 
   & Self-Identification - Collection & -.46 \; (0.54) \\ 
   & Self-Identification - Other & 1.12 \; (0.31)^{***} \\ 
   & AN Ranking - Included & .25 \; (0.35) \\ 
   & AN Ranking - Dropped & .51 \; (0.50) \\ 
   & Founder name in Museum name & .09 \; (0.28) \\ 
   & Exhibition any & -.22 \; (0.27) \\ 
   \multicolumn{3}{l}{\textbf{Environment}} \\ 
 & PM density (country) & .63 \; (0.35) \\ 
   & PM density$^{2}$ (country) & -.03 \; (0.02) \\ 
   & Pop. (millions) within 10km & .27 \; (0.09)^{**} \\ 
   & Nbr PM within 10km & .26 \; (0.08)^{***} \\ 
   & Nbr PM (10km) * Pop (10km) & -.09 \; (0.03)^{**} \\ 
   & Great Recession (2008/09) & -1.61 \; (1.01) \\ 
   & Covid Pandemic (2020/21) & .39 \; (0.29) \\ 
   \hline
 & Museum-years & 6096 \\ 
   & Closures & 68 \\ 
   & log. Likelihood & -338.36 \\ 
   & AIC & 712.73 \\ 
   & BIC & 752.68 \\ 
   \hline 
 \multicolumn{3}{l}{\footnotesize{standard errors in parantheses.\textsuperscript{***}p $<$ 0.001;\textsuperscript{**}p $<$ 0.01;\textsuperscript{*}p $<$ 0.05.}}
\end{tabular}
\caption{Cox Proportional Hazards Regression Results} 
\label{tbl:t_reg_coxph}
\end{table}
